Structured and decorated cospans

### 2019-06-14 cospans.tex
new title
tiny small edits notation

% An equivalence of compositional frameworks
% John Baez, Kenny Courser and Christina Vasilakopoulou
% 2019/09/11 - KC
\documentclass{amsart}
\input{Equiv_preamble.tex}
\usepackage[foot]{amsaddr}

\title{An equivalence of compositional frameworks}

@@

\begin{itemize}
\item {\chris Would a title like `An equivalence of compositional frameworks for networks' or `An equivalence of compositional network frameworks' be more informative? Otherwise, compositional framework on its own doesn't say much!}
\item {\chris Discuss notation for Decorated and Structured cospan double categories one last time? :)}
\item {\chris Notation between \cref{Equiv} and \cref{thm:decoratedcospans} right now does not match! Need to fix. Slightly prefer a,b,c for objects of A, then $a'$ and $b'$ for other objects, and x an object of the category F(c) namely the decoration. The previously used `d' is slightly confusing around all these a's, b's and c's that are in a different category. Also I prefer $a$ and $b$ rather than $a_1$ and $a_2$.}
%\item {\chris There might be a way to completely hide the details of version 'fibres have, reindexing preserve' if that's what we want to do.}
\end{itemize}

@@

\begin{proof}[Proof of \cref{Equiv}]
Recall that the double category of decorated cospans $\dcsp{F}$ has objects and vertical 1-morphisms those of $\A$, horizontal 1-cells $a\tickar b$ are cospans $\cspn{a}{c}{b}{}{}$ in $\A$ along with $x\in F(c)$, and 2-morphisms are cospan maps $k\colon c\to c'$ together with a morphism $(Fk)(x)\to x'$, see \cref{eq:FCsp2morph}.

@@

Using this functor $L_F$ between finitely cocomplete categories that preserves all colimits that exist (as a left adjoint), we can construct the double category of structured cospans $\scsp{L_F}{\inta F}$. Its objects and vertical morphisms are again those of the category $\A$, whereas horizontal 1-cells $a\tickar b$ as in \cref{eq:structuredcospan} are now cospans of the form $\cspn{L_F(a)}{v}{L_F(b)}{}{}$ in the Grothendieck category $\inta F$. Explicitly, they consist of two pairs of morphisms 
\begin{equation}\label{eq:scsphor1cell}
 (a,\bot_a)\xrightarrow{\scalebox{0.7}{$\begin{cases}i\colon a\to c &\textrm{in }\A \\!\colon F(i)(\bot_a)\to x &\textrm{in }F(c)\end{cases}$}}(c,x)\xleftarrow{\scalebox{0.7}{$\begin{cases}o\colon b\to c &\textrm{in }\A \\!\colon F(o)(\bot_b)\to x &\textrm{in }F(c)\end{cases}$}}(b,\bot_b)
\end{equation}
where $x\in F(c)$, according to \cref{def:GrothCat}. Finally, the 2-morphisms in this double category are as described in \cref{eq:2cellsStrCsp}, in this context fully unravelled below:
\begin{displaymath}
 \begin{tikzcd}[sep=1.5in,ampersand replacement=\&]
 (a,\bot_a)\ar[r,"{\begin{cases}i\colon a\to c &\textrm{in }\A \\!\colon F(i)(\bot_a)\to x &\textrm{in }F(c)\end{cases}}"]\ar[d,"{\begin{cases}f\colon a\to a' &\textrm{in }\A \\\chi_a\colon F(f)(\bot_a)\cong \bot_{a'} &\textrm{in }F(a')\end{cases}}"description] \& (c,x) \ar[d,"{\begin{cases}k\colon c\to c' &\textrm{in }\A \\ \iota\colon F(k)(x)\to x' &\textrm{in }F(c')\end{cases}}"description] \& (b,\bot_b)\ar[l,"{\begin{cases}o\colon b\to c &\textrm{in }\A \\!\colon F(o)(\bot_b)\to x &\textrm{in }F(c)\end{cases}}"']\ar[d,"{\begin{cases}g\colon b\to b' &\textrm{in }\A \\\chi_b\colon F(g)(\bot_b)\cong \bot_{b'} &\textrm{in }F(b')\end{cases}}"description] \\
 (a',\bot_{a'})\ar[r,"{\begin{cases}i'\colon a'\to c' &\textrm{in }\A \\!\colon F(i')(\bot_{a'})\to x' &\textrm{in }F(c')\end{cases}}"'] \& (c',x') \& (b',\bot_{b'})\ar[l,"{\begin{cases}o'\colon b'\to c' &\textrm{in }\A \\!\colon F(o')(\bot_{b'})\to x' &\textrm{in }F(c')\end{cases}}"]
 \end{tikzcd}
\end{displaymath}
where the outside vertical legs come from the definition of $L_F$ on arrows, \cref{eq:Lonarrows}. 
{\chris The above diagram might be a bit overwhelming, but all info is there. Choose which parts are required for a smooth proof!} {\chris Also, iota and the letter i look alarmingly similar. Should we change iota to some other distinctive greek letter?}
The square commutativities translate to $k\circ i=i'\circ f$ and $k\circ o=o'\circ g$ in $\A$, and also by composition in the Grothendieck category, to
\begin{gather}\label{eq:Grothcommutativity}
 F(k\circ i)(\bot_a)\cong Fk(Fi(\bot_a))\xrightarrow{Fk(!)}Fk(x)\xrightarrow{\iota}x'= \\
 F(i'\circ f)(\bot_a)\cong Fi'(Ff(\bot_a))\xrightarrow{Fi'(\chi_a)}Fi'(\bot_{a'})\xrightarrow{!}x'\nonumber
\end{gather}
in the category $F(c')$. However, since all maps are unique in the above equality, emanating from initial objects (since reindexing functors preserve those), this gives no extra conditions for the morphisms involved; similarly for the equality including $o, o'$.

In order to prove that there is a double equivalence (\cref{ShulDubEquiv}) between $\dcsp{F}$ and $\scsp{L_F}{\inta F}$, we define a %n identity-on-objects and vertical morphism
double functor
\begin{displaymath}
\mathbb{E}\colon\scsp{L_F}{\inta F} \longrightarrow\dcsp{F}
\end{displaymath}
as follows. The object component of $\mathbb{E}=(\mathbb{E}_0,\mathbb{E}_1)$ is $\mathbb{E}_0 = \id_{\mathsf{A}}$ since both double categories have $\mathsf{A}$ as their vertical category; trivially, $\mathbb{E}_0$ is an equivalence of categories. Given a horizontal 1-cell in $\scsp{L_F}{\inta F}$ like \cref{eq:scsphor1cell}, the arrow component $\mathbb{E}_1$ of the double functor simply maps it to the decorated cospan
\begin{displaymath}
 a\xrightarrow{\; i \;}c\xleftarrow{\; o \;}b\;\textrm{ with decoration }x\in F(c)
\end{displaymath}
Notice that this really is a bijective correspondence since the unique maps from the initial objects in the fibres provide no extra information. Finally, given a 2-morphism of $L_F$-structured cospans as described above, $\mathbb{E}_1$ maps it to the underlying cospan 2-morphism
\begin{displaymath}
 \begin{tikzcd}
a\ar[r,"i"]\ar[d,"f"'] & c\ar[d,"k"] & b\ar[l,"o"']\ar[d,"g"] \\
a'\ar[r,"i'"']& c' & b'\ar[l,"o'"]
 \end{tikzcd}
\end{displaymath}
 in $\A$ along with the map $\iota\colon Fk(x)\to x'$ in $F(c')$, namely a decorated cospan 2-morphism as per \cref{eq:FCsp2morph}. Once again, this is a bijective correspondence since, as discussed above, the commutativity \cref{eq:Grothcommutativity} holds automatically by initiality of the domain.
 {\chris Christina commented out big chunks of proof. They are right below if we want to revive parts of them, if we think the reader needs deeper level of detail.}

@@

To show that the double functor $\mathbb{E}$ is fully faithful, we need to show that the map  $$\mathbb{E}_1 \colon _f { _L \mathbb{C}\textnormal{sp}(\mathsf{X})}_g(M,N) \to {_{\mathbb{E}(f)} {F\mathbb{C}\textnormal{sp}}_{\mathbb{E}(g)}}(\mathbb{E}(M),\mathbb{E}(N))$$ is bijective for arbitrary vertical 1-morphisms $f$ and $g$ and horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$.  Consider a 2-morphism in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ with horizontal source and target $M$ and $N$, respectively and vertical source and target $f$ and $g$, respectively:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,0) {$x$};
\node (C) at (2,0) {$L(c_2)$};
\node (A') at (0,-1) {$L(c_1^\prime)$};
\node (B') at (1,-1) {$x^\prime$};
\node (C') at (2,-1) {$L(c_2^\prime)$};
\node (D) at (1,0.5) {$M$};
\node (E) at (-1,-0.5) {$f$};
\node (F) at (1,-1.5) {$N$};
\node (G) at (3,-0.5) {$g$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A') edge node[above]{$i^\prime$} (B')
(C') edge node[above]{$o^\prime$} (B')
(A) edge node [left]{$L(f)$} (A')
(B) edge node [left]{$\alpha$} (B')
(C) edge node [right]{$L(g)$} (C');
\end{tikzpicture}
\]
Thus the set $$_f { _L \mathbb{C}\textnormal{sp}(\mathsf{X})}_g(M,N)$$ consists of triples $$(f,\alpha,g)$$ rendering the above diagram commutative where $f$ and $g$ are morphisms of $\mathsf{A}$ and $\alpha$ is a morphism of $\mathsf{X}$. The image of the above 2-morphism under the double functor $\mathbb{E}$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,0) {$R(x)$};
\node (C) at (2,0) {$c_2$};
\node (A') at (0,-1) {$c_1^\prime$};
\node (B') at (1,-1) {$R(x^\prime)$};
\node (C') at (2,-1) {$c_2^\prime$};
\node (D) at (1,0.5) {$x \in F(R(x))$};
\node (D') at (1,-1.5) {$x^\prime \in F(R(x^\prime))$};
\node (E) at (1,1) {$\mathbb{E}(M)$};
\node (F) at (-1,-0.5) {$\mathbb{E}(f)$};
\node (G) at (1,-2) {$\mathbb{E}(N)$};
\node (H) at (3,-0.5) {$\mathbb{E}(g)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$R(i)\eta_{c_1}$} (B)
(C) edge node[above]{$R(o)\eta_{c_2}$} (B)
(A') edge node[above]{$R(i^\prime)\eta_{c_1^\prime}$} (B')
(C') edge node[above]{$R(o^\prime)\eta_{c_2^\prime}$} (B')
(A) edge node [left]{$f$} (A')
(B) edge node [left]{$R(\alpha)$} (B')
(C) edge node [right]{$g$} (C');
\end{tikzpicture}
\]
together with a morphism $\iota \colon F(R(\alpha))(x) \to x^\prime$ of $F(R(x^\prime))$.
Thus the set $$_{\mathbb{E}(f)} {F\mathbb{C}\textnormal{sp}}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ consists of 4-tuples $$(f,R(\alpha),g,\iota)$$ rendering the above diagram commutative and where $f,g$ and $R(\alpha)$ are morphisms of $\mathsf{A}$ and $\iota$ is a morphism in $F(R(x'))$. The morphisms $R(\alpha) \colon R(x) \to R(x^\prime)$ and $\iota \colon F(R(\alpha))(x) \to x^\prime$ together determine the morphism $\alpha \colon x \to x^\prime$ in $\mathrm{X}$ and conversely; given two objects $x=(c,x \in F(c))$ and $x^\prime=(c^\prime,x^\prime \in F(c^\prime))$ of $\mathsf{X}=\inta{F}$, a morphism from $\alpha \colon x \to x^\prime$ is a pair $$(h \colon c \to c^\prime, \iota \colon F(h)(x) \to x^\prime)$$ where $h \colon c \to c^\prime$ is given by $R(\alpha) \colon R(x) \to R(x^\prime)$. This shows that $\mathbb{E}$ is fully faithful. \textbf{At least in my favorite example...}
\end{comment}
Functoriality of $\mathbb{E}_1$ can be verified, and moreover $(\mathbb{E}_0,\mathbb{E}_1)$ indeed define a strong double functor: there exist natural isomorphisms
\begin{gather*}
 \mathbb{E}(M) \odot \mathbb{E}(N) \xrightarrow{\sim} \mathbb{E}(M \odot N) \\
U_{\mathbb{E}(c,x)} \xrightarrow{\sim} \mathbb{E}(U_{(c,x)})
\end{gather*}
for any pair of composable horizontal 1-cells $M$ and $N$ and any object $(c,x)$ of $\scsp{L_F}{\inta F}$
{\chris in progress}

>>>>

% Structured and decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% 2019/09/11 - KC
\documentclass{amsart}
\input{Equiv_preamble.tex}
\usepackage[foot]{amsaddr}

\title{Structured and decorated cospans}

@@

\begin{itemize}
\item {\chris Notation between \cref{Equiv} and \cref{thm:decoratedcospans} right now does not match! Need to fix. Slightly prefer a,b,c for objects of A, then $a'$ and $b'$ for other objects, and x an object of the category F(c) namely the decoration. The previously used `d' is slightly confusing around all these a's, b's and c's that are in a different category. Also I prefer $a$ and $b$ rather than $a_1$ and $a_2$.}

{\chris After a brief discussion in John's office, for \cref{Equiv} I used $a,b,c$ for the feet and $m,n$ for the apices so we can serially compose. Of course can change as we like.}
%\item {\chris There might be a way to completely hide the details of version 'fibres have, reindexing preserve' if that's what we want to do.}

\end{itemize}

@@

\begin{proof}[Proof of \cref{Equiv}]
Recall that the double category of decorated cospans $\dcsp{F}$ has objects and vertical 1-morphisms those of $\A$, horizontal 1-cells $a\tickar b$ are cospans $\cspn{a}{m}{b}{}{}$ in $\A$ along with $x\in F(m)$, and 2-morphisms are cospan maps $k\colon m\to m'$ together with a morphism $(Fk)(x)\to x'$, see \cref{eq:FCsp2morph}.

@@

Using this functor $L_F$ between finitely cocomplete categories that preserves all colimits that exist (as a left adjoint), we can construct the double category of structured cospans $\scsp{L_F}{\inta F}$. Its objects and vertical morphisms are again those of the category $\A$, whereas horizontal 1-cells $a\tickar b$ as in \cref{eq:structuredcospan} are now cospans of the form $\cspn{L_F(a)}{v}{L_F(b)}{}{}$ in the Grothendieck category $\inta F$. Explicitly, they consist of two pairs of morphisms 
\begin{equation}\label{eq:scsphor1cell}
 (a,\bot_a)\xrightarrow{\scalebox{0.7}{$\begin{cases}i\colon a\to m &\textrm{in }\A \\!\colon F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}$}}(m,x)\xleftarrow{\scalebox{0.7}{$\begin{cases}o\colon b\to m &\textrm{in }\A \\!\colon F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}$}}(b,\bot_b)
\end{equation}
where $x\in F(m)$, according to \cref{def:GrothCat}. Finally, the 2-morphisms in this double category are as described in \cref{eq:2cellsStrCsp}, in this context fully unravelled below:
\begin{displaymath}
 \begin{tikzcd}[sep=1.5in,ampersand replacement=\&]
 (a,\bot_a)\ar[r,"{\begin{cases}i\colon a\to m &\textrm{in }\A \\!\colon F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}}"]\ar[d,"{\begin{cases}f\colon a\to a' &\textrm{in }\A \\\chi_a\colon F(f)(\bot_a)\cong \bot_{a'} &\textrm{in }F(a')\end{cases}}"description] \& (m,x) \ar[d,"{\begin{cases}k\colon m\to m' &\textrm{in }\A \\ \iota\colon F(k)(x)\to x' &\textrm{in }F(m')\end{cases}}"description] \& (b,\bot_b)\ar[l,"{\begin{cases}o\colon b\to m &\textrm{in }\A \\!\colon F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}}"']\ar[d,"{\begin{cases}g\colon b\to b' &\textrm{in }\A \\\chi_b\colon F(g)(\bot_b)\cong \bot_{b'} &\textrm{in }F(b')\end{cases}}"description] \\
 (a',\bot_{a'})\ar[r,"{\begin{cases}i'\colon a'\to m' &\textrm{in }\A \\!\colon F(i')(\bot_{a'})\to x' &\textrm{in }F(m')\end{cases}}"'] \& (m',x') \& (b',\bot_{b'})\ar[l,"{\begin{cases}o'\colon b'\to m' &\textrm{in }\A \\!\colon F(o')(\bot_{b'})\to x' &\textrm{in }F(m')\end{cases}}"]
 \end{tikzcd}
\end{displaymath}
where the outside vertical legs come from the definition of $L_F$ on arrows, \cref{eq:Lonarrows}. 
{\chris The above diagram might be a bit overwhelming, but all info is there. Choose which parts are required for a smooth proof!} {\chris Also, iota and the letter i look alarmingly similar. Should we change iota to some other distinctive greek letter?}
The square commutativities translate to $k\circ i=i'\circ f$ and $k\circ o=o'\circ g$ in $\A$, and also by composition in the Grothendieck category, to
\begin{gather}\label{eq:Grothcommutativity}
 F(k\circ i)(\bot_a)\cong Fk(Fi(\bot_a))\xrightarrow{Fk(!)}Fk(x)\xrightarrow{\iota}x'= \\
 F(i'\circ f)(\bot_a)\cong Fi'(Ff(\bot_a))\xrightarrow{Fi'(\chi_a)}Fi'(\bot_{a'})\xrightarrow{!}x'\nonumber
\end{gather}
in the category $F(m')$. However, since all maps are unique in the above equality, emanating from initial objects (since reindexing functors preserve those), this gives no extra conditions for the morphisms involved; similarly for the equality including $o, o'$.

In order to prove that there is a double equivalence (\cref{ShulDubEquiv}) between $\dcsp{F}$ and $\scsp{L_F}{\inta F}$, we define a %n identity-on-objects and vertical morphism
double functor
\begin{displaymath}
\mathbb{E}\colon\scsp{L_F}{\inta F} \longrightarrow\dcsp{F}
\end{displaymath}
as follows. The object component of $\mathbb{E}=(\mathbb{E}_0,\mathbb{E}_1)$ is $\mathbb{E}_0 = \id_{\mathsf{A}}$ since both double categories have $\mathsf{A}$ as their vertical category; trivially, $\mathbb{E}_0$ is an equivalence of categories. Given a horizontal 1-cell in $\scsp{L_F}{\inta F}$ like \cref{eq:scsphor1cell}, the arrow component $\mathbb{E}_1$ of the double functor simply maps it to the decorated cospan
\begin{displaymath}
 a\xrightarrow{\; i \;}m\xleftarrow{\; o \;}b\;\textrm{ with decoration }x\in F(m)
\end{displaymath}
Notice that this really is a bijective correspondence since the unique maps from the initial objects in the fibres provide no extra information. Finally, given a 2-morphism of $L_F$-structured cospans as described above, $\mathbb{E}_1$ maps it to the underlying cospan 2-morphism
\begin{displaymath}
 \begin{tikzcd}
a\ar[r,"i"]\ar[d,"f"'] & m\ar[d,"k"] & b\ar[l,"o"']\ar[d,"g"] \\
a'\ar[r,"i'"']& m' & b'\ar[l,"o'"]
 \end{tikzcd}
\end{displaymath}
 in $\A$ along with the map $\iota\colon Fk(x)\to x'$ in $F(m')$, namely a decorated cospan 2-morphism as per \cref{eq:FCsp2morph}. Once again, this is a bijective correspondence since, as discussed above, the commutativity \cref{eq:Grothcommutativity} holds automatically by initiality of the domain.
 {\chris Christina commented out big chunks of proof. They are right below if we want to revive parts of them, if we think the reader needs deeper level of detail.}

@@

To show that the double functor $\mathbb{E}$ is fully faithful, we need to show that the map  $$\mathbb{E}_1 \colon _f { _L \mathbb{C}\textnormal{sp}(\mathsf{X})}_g(M,N) \to {_{\mathbb{E}(f)} {F\mathbb{C}\textnormal{sp}}_{\mathbb{E}(g)}}(\mathbb{E}(M),\mathbb{E}(N))$$ is bijective for arbitrary vertical 1-morphisms $f$ and $g$ and horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$.  Consider a 2-morphism in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ with horizontal source and target $M$ and $N$, respectively and vertical source and target $f$ and $g$, respectively:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,0) {$x$};
\node (C) at (2,0) {$L(c_2)$};
\node (A') at (0,-1) {$L(c_1^\prime)$};
\node (B') at (1,-1) {$x^\prime$};
\node (C') at (2,-1) {$L(c_2^\prime)$};
\node (D) at (1,0.5) {$M$};
\node (E) at (-1,-0.5) {$f$};
\node (F) at (1,-1.5) {$N$};
\node (G) at (3,-0.5) {$g$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A') edge node[above]{$i^\prime$} (B')
(C') edge node[above]{$o^\prime$} (B')
(A) edge node [left]{$L(f)$} (A')
(B) edge node [left]{$\alpha$} (B')
(C) edge node [right]{$L(g)$} (C');
\end{tikzpicture}
\]
Thus the set $$_f { _L \mathbb{C}\textnormal{sp}(\mathsf{X})}_g(M,N)$$ consists of triples $$(f,\alpha,g)$$ rendering the above diagram commutative where $f$ and $g$ are morphisms of $\mathsf{A}$ and $\alpha$ is a morphism of $\mathsf{X}$. The image of the above 2-morphism under the double functor $\mathbb{E}$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,0) {$R(x)$};
\node (C) at (2,0) {$c_2$};
\node (A') at (0,-1) {$c_1^\prime$};
\node (B') at (1,-1) {$R(x^\prime)$};
\node (C') at (2,-1) {$c_2^\prime$};
\node (D) at (1,0.5) {$x \in F(R(x))$};
\node (D') at (1,-1.5) {$x^\prime \in F(R(x^\prime))$};
\node (E) at (1,1) {$\mathbb{E}(M)$};
\node (F) at (-1,-0.5) {$\mathbb{E}(f)$};
\node (G) at (1,-2) {$\mathbb{E}(N)$};
\node (H) at (3,-0.5) {$\mathbb{E}(g)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$R(i)\eta_{c_1}$} (B)
(C) edge node[above]{$R(o)\eta_{c_2}$} (B)
(A') edge node[above]{$R(i^\prime)\eta_{c_1^\prime}$} (B')
(C') edge node[above]{$R(o^\prime)\eta_{c_2^\prime}$} (B')
(A) edge node [left]{$f$} (A')
(B) edge node [left]{$R(\alpha)$} (B')
(C) edge node [right]{$g$} (C');
\end{tikzpicture}
\]
together with a morphism $\iota \colon F(R(\alpha))(x) \to x^\prime$ of $F(R(x^\prime))$.
Thus the set $$_{\mathbb{E}(f)} {F\mathbb{C}\textnormal{sp}}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ consists of 4-tuples $$(f,R(\alpha),g,\iota)$$ rendering the above diagram commutative and where $f,g$ and $R(\alpha)$ are morphisms of $\mathsf{A}$ and $\iota$ is a morphism in $F(R(x'))$. The morphisms $R(\alpha) \colon R(x) \to R(x^\prime)$ and $\iota \colon F(R(\alpha))(x) \to x^\prime$ together determine the morphism $\alpha \colon x \to x^\prime$ in $\mathrm{X}$ and conversely; given two objects $x=(c,x \in F(c))$ and $x^\prime=(c^\prime,x^\prime \in F(c^\prime))$ of $\mathsf{X}=\inta{F}$, a morphism from $\alpha \colon x \to x^\prime$ is a pair $$(h \colon c \to c^\prime, \iota \colon F(h)(x) \to x^\prime)$$ where $h \colon c \to c^\prime$ is given by $R(\alpha) \colon R(x) \to R(x^\prime)$. This shows that $\mathbb{E}$ is fully faithful. \textbf{At least in my favorite example...}
\end{comment}
Functoriality of $\mathbb{E}_1$ can be verified, and moreover $(\mathbb{E}_0,\mathbb{E}_1)$ indeed define a strong double functor: there exist natural isomorphisms
\begin{gather*}
 \mathbb{E}(M) \odot \mathbb{E}(N) \xrightarrow{\sim} \mathbb{E}(M \odot N) \\
U_{\mathbb{E}(m,x)} \xrightarrow{\sim} \mathbb{E}(U_{(m,x)})
\end{gather*}
for any pair of composable horizontal 1-cells $M$ and $N$ and any object $(m,x)$ of $\scsp{L_F}{\inta F}$
{\chris in progress}
